Dynein project log

### 2016-10-01 thesis_stuff/thesis_stuff.tex
teach make to build figures I hope and add pretty figure
Add new rate scheme based on Winch paper.

@@

\subsection{Imamula Stepping Model}
This is an older (2007) paper presenting a chemical model. It gives more MT dissociation constants for several different dyneins, and averages them as: $K_{d,pre} = 0.2uM$, $K_{d,post} > 10uM$. They determine these by adding a known concentration of Dynein apo, ATP, ADP-Pi or ADP, adding microtubules, removing MT-Dynein dimers and remeasuring concentration. These parameters are good in that equilibrium constants (as opposed to rate constants) \textit{don't} take into account kinetics, only free energy change...right?\\

>>>>

\subsection{Arrhenius Rate}
Papers often supply rate constants for various transitions. Our model uses Arhennius-type rates which take into account the change in conformational energy from switching equilibrium angles, so we must
convert between these two systems:

\begin{align*}
  k_{bind} &= Ae^{-\beta(\Delta G_{bind} + \Delta G_{conf})}\\
  k_{bind} &= \left(Ae^{-\beta\Delta G_{bind}}\right)e^{-\beta\Delta G_{conf}}\\
  k_{bind} &= Be^{-\beta\Delta G_{conf})}\hspace{2cm}\mbox{B constant at constant T}\\
  \left<k_{bind}\right> &= \left<Be^{-\beta\Delta G_{conf}}\right>\\
  \left<k_{bind}\right> &= Be^{-\beta\Delta \left<G_{conf}\right>}\\
  \left<\Delta G_{conf}\right> &= \left(4-2\right)\left(\frac{1}{2}k_BT\right) = \beta^{-1}\\
  \left<k_{bind}\right> &= Be^{-1}\\
  \rightarrow B &= \frac{k_{bind}}{e}\\
\end{align*}

@@

\subsection{Imamula Stepping Model}
This is an older (2007) paper presenting a chemical model and giving rate constants for MT un/binding. Averages are: $K_{d,pre} = 0.2uM$, $K_{d,post} > 10uM$. They determine these by adding a known concentration of monomeric Dynein apo, ATP, ADP-Pi or ADP, adding microtubules, removing MT-Dynein dimers and remeasuring concentration. These parameters are good in that equilibrium constants (as opposed to rate constants) \textit{don't} take into account kinetics, only free energy change...right?\\

Also, the paper says that axonemal dyneins have multiple motor domains, i.e aren't dimers, so that changes the results from the Lin paper. The binding angle is probably valid, though.\\
